Demand-aware geo-distributed placement for low latency

### 2015-07-05 auspice/design.tex
added shrink, auspice, first draft background, intro edited

\vsp
\section{ \auspice\ design \& implementation}
\label{sec:design}

%In this section, we present \auspice, a massively scalable global record service designed for high mobility. We begin by describing how the envisioned service enables endpoint mobility, and the requirements in order to realize that vision.

@@

Our goal is to design a distributed system that meets the following requirements:

{\bf (1) Low lookup latency}: Replicas of a key should be placed close to end-users accessing it so as to minimize user-perceived response times.

%An implicit goal here is to not only support use-cases like above but also to enable other architectural proposals that involve routers late-binding records to addresses near the destination \cite{serval,MobilityFirst-UMASS}; enabling seamless mid-connection mobility \cite{Migrate,ECCP}, etc., so that any endpoint or router gets the feel of the lookup service being located tens of milliseconds away.

{\bf (2) Resource cost}: The design must ensure low replication cost. A naive way to minimize lookup latencies is to replicate every record at every possible location, however high mobility means high update rates, so the cost of pushing each update to every replica would be prohibitive. Worse, load hotspots can actually degrade lookup latencies.

@@

{\bf (4) Consistency}: The design must provide flexible consistency semantics as desired by an application.

@@

\subsection{\auspice's geo-distributed design}
\label{sec:design_overview}

To address the above goals, the \auspice\  is designed as a massively geo-distributed key-value store. The geo-distribution is essential to the latency and availability goals while the key-value API is chosen for its popularity among today's web services. Each {\em record} in \auspice\ is associated with a globally unique identifier (GUID) that is the record's primary key. A record contains an associative array of key-value pairs, wherein each key $K_i$ is a string and the value $V_i$ may be a string, a primitive type, or recursively a key-value pair, as shown below.

@@

@@

%For the former, it suffices to think of a {\em record} as a domain record, a {\em record} as the associated zone file, and a {\em server} as analogous to a DNS server. For ease of exposition, we assume one server per geo-location.

%\subsection{\auspice's geo-distributed design}

\begin{figure}[t]
\centering
\vspace{-0.3in}
\includegraphics[scale=0.33]{gns-dns/gnrs.pdf}
\vspace{-0.35in}
\caption{Geo-distributed servers in \auspice.  Replica-controllers  (logically separate from active replicas) decide placement of active replicas and active replicas handle requests from end-users. N1 is a globally popular record and is replicated globally; record N2 is  popular in select regions and is replicated in those regions.}
\vspace{-0.2in}
\label{fig:auspice}
\end{figure}

At the core of \auspice\ is a placement engine that achieves the latency, cost, and availability goals by adapting the number and locations of replicas of each record in accordance with (1) the lookup and update request rates for the record, (2) the geo-distribution of requests for the record, and (3) the aggregate request load across all records.

%The key to ensuring high availability and flexible consistency is a two-tier consensus engine for each record; the first ``control'' tier infrequently recomputes and migrates the current set of replicas of each record, and the second ``data'' tier upon each write or read coordinates with other replicas to ensure the necessary consistency semantics.% In addition to the placement algorithm, the design and implementation challenges we address include managing a very large number of parallel Paxos instances (one per record per tier); correctly changing Paxos group membership in a live system; efficiently routing client requests;  TBD\tbd{Need to say why challenging somewhere clearly}.

Figure \ref{fig:auspice} illustrates the placement engine. Each record is associated with a fixed number, $F$, of  \emph{replica-controllers} and a variable number of  {\em active replicas} of the corresponding record. The record's replica-controllers are computed using consistent hashing to select $F$ consecutive or otherwise deterministic nodes along the ring {\em onto} which the hash function maps records and nodes. The replica-controllers are responsible only for determining the number and locations of the active  replicas, and the actives replicas are responsible for maintaining the actual record and processing client requests. The replica-controllers implement a replicated state machine using Paxos \cite{LamportPaxos} in order to maintain a consistent view of the current set of active replicas.

%The key insight in \auspice\ is a placement engine to compute the number and locations of replicas of a record  based on the lookup to update ratio of the record,  the geo-distribution of its demand, and the aggregate request load on the system.

%
%At an abstract level, \auspice\ design can be described as consisting of two planes: a ``control plane'' which determines the locations at which each record is replicated, and a ``data plane''  consisting of  replicas of records whose function is to handle address lookups and updates for end-users.  Physically, both these planes run across the set of servers on which \auspice\ is deployed. 
%
%
%The role of the control plane for a record is handled by a fixed number, $M$, of  \emph{replica-controllers}. The number and locations of the replica-controllers is fixed and is computed using $M$ well-known consistent hash functions each of which maps the record to a server location. The replica-controllers implement a replicated state machine using Paxos \cite{LamportPaxos} so as to maintain a consistent view of the current set of active replicas despite failures. 
%

%The control plane periodically runs a placement algorithm and places a record based on the inferred pockets of demand for that record, the lookup-to-update ratio of the record, and the aggregate system load so as to achieve low lookup latency, low update cost, and desired level of availability.

% achieve low response times, low update costs, and high availability.
%based on the geo-locality of demand for that record while mitigating load hotspots across all locations.

%The key insight in \auspice\ is a placement engine to compute the number and locations of resolver replicas for a record based on the geo-locality of demand for that record while mitigating load hotspots across all locations.

@@

%Figure \ref{fig:auspice} illustrates the architecture of \auspice.  Each record is associated with a fixed number, $M$, of  \emph{replica-controllers} and a variable number of  {\em active replicas} of the corresponding resolver. The locations of the replica-controllers is fixed and computed using $M$ well-known consistent hash functions each of which maps the record to a server location. The replica-controllers form the ``control plane'' and are responsible only for determining the number and locations of active replicas, and the active replicas are responsible for maintaining resource records and responding to lookup and update requests.

@@

A record's replica-controllers compute its active replica locations in a {\em demand-aware} manner. This computation proceeds in epochs as follows. At creation time, the active replicas are chosen to be physically at the same locations as the corresponding replica-controllers. In each epoch, the replica-controllers obtain from each active replica a summarized load report that contains the request rates for that record from different {regions} as seen by that replica. Here, {\em regions} partition users into non-overlapping groups that capture locality, e.g., IP prefixes or a geographic  partitioning based on cities; and the {\em load report} is a spatial vector of request rates as seen by the replica. The replica-controllers aggregate these load reports to obtain a concise spatial distribution of all requests for the record.

\eat{
The replica-controllers execute Paxos to compute the placement decision in a coordinated manner for each record. During periods of graceful execution, only one replica-controller (the Paxos coordinator) actually invokes the mapping algorithm while the others simply accept its proposed placement; consensus ensures that the replica-controllers maintain a consistent view of the current set of active replicas despite failures.
}

%\begin{figure}[t]
%\begin{center}
%%\includegraphics[width=3in, height=2.4in]{Auspice-arch/Slide1}
%\includegraphics[width=3in]{graph/slide2SS}
%\vspace{-0.2in}
%\caption{\auspice\ design: Clients send typical requests to nearby active replicas of resolvers. Replica-controllers compute the number and locations of active replicas for each record based on load reports in each epoch.}
%\vspace{-0.2in}
%\label{fig:arch}
%\end{center}
%\end{figure}
\vsp
\subsubsection{Demand-aware replica placement} 
\label{sec:placement}

In each epoch, the replica-controllers use a {placement algorithm} that takes as input the aggregated load reports and capacity constraints at servers to determine the number and locations of active replicas for each record so as to minimize client-perceived latency. We have formalized this {\em global} optimization problem as a mixed-integer program and shown it to be computationally hard.  As our focus is on simple, practical algorithms, we defer the details of the optimization approach \cite{techreport}, using it only as a benchmark in small-scale experiments with \auspice's heuristic algorithm.

@@

\auspice's placement algorithm is a simple heuristic  and can be run {\em locally} by each replica-controller. The placement algorithm computes the number of replicas using the lookup-to-update ratio of a record in order to limit the update cost to within a small factor of the lookup cost. The number of replicas is always kept more than the minimum number needed to meet the availability objective under failures.   The location of these replicas are decided to minimize lookup latency by placing a fraction of replicas close to pockets of high demand for that record while placing the rest randomly so as to balance the potentially conflicting goals of reducing latency and balancing load among servers.
%The location of these replicas are decided partly based on the locality of demand, while the rest of the replicas are placed randomly in order to achieve a good tradeoff between locality-awareness and load-balance.

Specifically, the placement algorithm computes the number of replicas for a record as ($F+ \beta r_i/w_i$), where $r_i$ and $w_i$ are the lookup and update rates of record $i$; $F$ is the minimum number of replicas needed to meet the availability goal (\S \ref{sec:design_goals}); and $\beta$ is a replication control parameter that is automatically determined by the system so as to trade off latency benefits of replication against update costs given capacity constraints as follows. In each epoch, the replica-controllers recompute $\beta$ so that the aggregate load in the system corresponds to a preset threshold utilization fraction $\mu$. For simplicity of exposition, suppose read and write operations impose the same load, and the total capacity across all servers (in reads/sec) is $C$. Then, $\beta$ is set so that  
\vsp
\begin{equation}
\mu C = \sum_i r_i  + \sum_i (F + \beta  \frac{r_i}{w_i}) w_i
\label{eq:mu}
\end{equation}
\vsp
\vsp

 where the right hand side represents the total load summed across all records. The first term in the summation above is the total read load and the second is the total write load. 
%\begin{equation}
%\beta = \frac{C\mu - M \sum_i W_i}{\sum_i R_i}- 1
%\label{eq:beta}
%\end{equation}
%It is straightforward to extend the above heuristic to scenarios where read and write operations impose unequal amounts of load on a server

Having computed $\beta$ as above, replica-controllers compute the locations of active replicas for record $i$ as follows. Out of the $F + \beta r_i/w_i$ total replicas, a fraction $\nu$ of replicas are chosen based on locality, i.e., replica-controllers use the spatial vector of load reports to select $\nu(F + \beta r_i/w_i)$ servers that are respectively the {closest} to the top $\nu(F + \beta r_i/w_i)$ regions sorted by demand for record $i$. The remaining $(1-\nu)(F + \beta r_i/w_i)$  are chosen randomly without repetition. The locality-based replicas above are chosen as the {\em closest} with respect to round-trip latency plus load-induced latency measured locally at each server. An earlier design chose them based on round-trip latency alone, but we found that adding load-induced latencies in this step (in addition to choosing the remaining replicas randomly) ensures better load balance and lowers overall client-perceived latency.
Our current prototype and system experiments fix the random perturbation knob $\nu$ to 0.5. We have since developed a slightly modified placement scheme that relieves the administrator from setting $\nu$ manually, automatically balancing locality-awareness and load to ensure low latencies \cite{techreport}. Thus, an administrator need only specify F and $\mu$ based on fault tolerance and aggressiveness of capacity utilization.

\auspice's replica placement scheme (Eq. \ref{eq:mu}) is designed to use a fraction $\mu$ of system-wide resources so as to make at least $F$ and at most $M$ replicas of each record, where $M$ is the total number of server locations. Thus, at light load, \auspice\ may replicate every record at every location, while under heavy load, it may create exactly $F$ replicas for all but the most popular records.

\subsubsection{Client request routing}
\label{sec:routing_client_requests}
A client request is routed from an end-host to a suitable server as follows. 
The set of all servers in an \auspice\ instance is known to each member server and can be obtained from a well-known location. 
When a client encounters a request for a record for the first time, it uses the known set of all servers and consistent hashing to determine the replica-controllers for that record and sends the request to the closest replica-controller. The replica-controller returns the set of active replicas for the record and the client resends the request to the closest active replica.  In practice, we expect replica-controllers to be contacted infrequently as the set of active replicas can be cached and reused until they change in some future epoch. %, and active replicas change across epochs only if the geo-locality of demand for the record changes significantly.
%client requests up to three active replicas to get a response.  A timeout value is set for every request sent and the request is sent to the next closest active replica on a timeout.

%To answer lookup requests, clients implement a TTL-based cache to store the records received.

%A client redirects end-users requests to a resolver chosen in a locality and load-aware manner. To achieve both these properties, clients maintain latency estimates to servers that reflect both network latency and server-load induced latency (or server latency). Among a set of resolvers,  a client always redirects requests to the closest server based on  the latency estimates.

%A client in \auspice\ redirects end-users requests to a resolver chosen in a locality and load-aware manner. To achieve both these properties, clients maintain latency estimates to servers that reflect both network latency and server-load induced latency (or server latency). Among a set of resolvers,  a client always redirects requests to the closest server based on  the latency estimates.  Network latency estimates change slowly and therefore every client maintains round-trip latency estimates to all servers using infrequent measurements. Server latency changes frequently due to dynamic workloads.  In an Internet scale deployment with tens of thousands of servers, maintaining server latency information would add significant overhead.  Hence, server latency  is maintained only for a smaller number of frequently contacted servers.

Network latency as well as server-load-induced latency help determine the closest replica at a client. Each client maintains an estimate of the round-trip latency to all servers using infrequent pings; an (as yet unimplemented) optimization to reduce the overhead of all-to-all pings is to use coordinate embedding, geo-IP, or measurement-driven techniques \cite{iplane}. To incorporate load-induced latency, the latency estimate to a server is passively measured as a moving average over lookups sent to that server. The client also maintains a timeout value based on the moving average and variance of the estimates.  If a lookup request sent to a server times out, the client infers that either the server or network route is congested, and it multiplicatively increases its latency estimate to that server by a fixed factor. Thus,  if multiple lookups sent to a server time out, the estimated latency shoots up and the client stops sending requests to that  server, which effectively acts as a more agile load-balancing policy in the request routing plane (complementing the replica placement plane above that operates in coarser-grained epochs).

@@

%The above proximity-based strategy can route both lookup (or read) and update (or write) requests for a record to any active replica. In order to ensure low lookup latency, it is important for them to be served locally from an active replica. This means that the onus of replica coordination in order to maintain any nontrivial consistency semantics falls on the update procedure. But why should we care about consistency when DNS and network protocols in general prize liveness over consistency\cite{consensus-routing}?

As a geo-distributed key-value store, \auspice\ must at least ensure this eventual consistency property: {\em all active replicas must eventually return the same value of the record and, in a single-writer scenario, this value must be the last update made by the (only) client}; ``eventually" means that there are no updates to a record and no replica failures for sufficiently long. Violating this property means that a client may be  indefinitely unable to obtain the the up-to-date value of the record even though the record is no longer being updated.

@@

\subsubsection{Replica reconfiguration policies}
\label{sec:reconf_policy}

>>>>

%!TEX root = sigc310-sharma.tex
\vsp
\section{ \auspice\ design \& implementation}
\label{sec:design}

%In this section, we present \auspice, a massively scalable global name service designed for high mobility. We begin by describing how the envisioned service enables endpoint mobility, and the requirements in order to realize that vision.

\begin{figure}[htbp]
	\figvsp
	\begin{center}
		\includegraphics[scale=0.29]{figure/4mobility.pdf}
		\vspace{-0.3in}
		\caption{Four kinds of mobility---(1) {\em pre-lookup}, (2) {\em connect-time}, (3) {\em individual}, (4) {\em simultaneous}---three of which require a global name service.} 
		\vspace{-0.2in}
		\label{fig:4mobility}
	\end{center}
	\vsp
\end{figure}

%\para{How GNS enables mobility}
{Our envisioned GNS enables endpoint mobility as shown in Figure \ref{fig:4mobility}. An endpoint A initiates communication with another endpoint B by querying the GNS for B's current addresses and connecting to one of them, thereby enabling {\em pre-lookup} mobility. If B moves after A's query but before before a connection has been mutually established via a three-way handshake ({\em connect-time} mobility), A times out and reverts back to the GNS. After a connection has been established, if either endpoint moves one at a time ({\em individual} mobility), it can re-synchronize the connection with a bilateral three-way handshake without relying upon the GNS (noting however that router-level late-binding proposals relying on a GNS-like infrastructure have also been proposed \cite{serval,MobilityFirst-UMASS}). If an endpoint moves mid-connection after the other endpoint has moved but before it could re-synchronize the connection ({\em simultaneous} mobility), one or both endpoint(s) eventually query the GNS and re-synchronize the connection.}

@@

\begin{figure}[htbp]
	\vsp
	\begin{center}
		\includegraphics[width=3in,height=2in]{figure/DNS-GNS.pdf}
		\figvsp
		\caption{\small{DNS vs. GNS: Auspice can be deployed as a managed DNS provider today (left) or as a GNS provider that provides resolution service for its customer GUIDs (right). Name certification services bind a human-readable name to a GUID and its GNS provider, and certificate search services can help index and distribute certificates from all certification services. Solid (dotted) lines represent frequent (infrequent) query paths for a given mobile destination. Except for the tightly controlled DNS root  service, all services above are designed to be purveyed competitively.} 
		}\label{fig:DNS_GNS}
	\end{center}
	\figvsp
\end{figure}

Much of the envisioned functionality of a GNS as above boils down to one over-arching distributed systems challenge: {\em any principal--endpoint or router--should get the look and feel of a high-availability name service that is nearby ($\approx$ few milliseconds) and rapidly returns up-to-date responses}. A more precise breakdown of goals is as follows.

{\bf (1) Time-to-connect performance}: The design must ensure low latencies  for name lookups to return up-to-date values, which determines the {\em time to connect} to a destination when the value being queried for is an address like above.  %Any  principal---endpoint or router---should get the feel of the lookup service being located just a few milliseconds away.

%An implicit goal here is to not only support use-cases like above but also to enable other architectural proposals that involve routers late-binding names to addresses near the destination \cite{serval,MobilityFirst-UMASS}; enabling seamless mid-connection mobility \cite{Migrate,ECCP}, etc., so that any endpoint or router gets the feel of the lookup service being located tens of milliseconds away.

{\bf (2) Resource cost}: The design must ensure low replication cost. A naive way to minimize lookup latencies is to replicate every name record at every possible location, however high mobility means high update rates, so the cost of pushing each update to every replica would be prohibitive. Worse, load hotspots can actually degrade lookup latencies.

@@

{\bf (4) Security}: The design must be robust to malicious users attempting to hijack or corrupt name records. The design must support flexible access control policies to ensure the desired level of privacy of name records.

{\bf (5) Federation}: The design must allow different name service providers to co-exist and for users to freely choose one or more preferred providers.

{\bf (6) Extensibility}: The design must be agnostic to how names, addresses, and resolution policies are represented by a future Internetwork. In particular, it should support flat names and a rich set of attributes and resolution policies for multi-homed mobility (e.g.,``prefer WiFi to cellular''), etc.

@@

%Figure \ref{fig:4mobility} illustrates the four kinds of mobility and shows how the GNS helps handle three of these---pre-lookup, connect-time, and simultaneous mobility. Only individual connection mobility can be handled bilaterally without the GNS (although router-level late-binding proposals relying on a GNS-like infrastructure have also been proposed \cite{serval,MobilityFirst-UMASS}). In addition to emphasizing the importance of the GNS for handling mobility, the figure also reinforces the first four of the six design goals laid out above.

\subsection{Design overview}
\label{sec:design_overview}

To address the above goals, the \auspice\ GNS is designed as a massively geo-distributed key-value store. The geo-distribution is essential to the latency and availability goals while the key-value API enables extensibility. Each {\em name record} in \auspice\ is associated with a globally unique identifier (GUID) that is the record's primary key. A name record contains an associative array of key-value pairs, wherein each key $K_i$ is a string and the value $V_i$ may be a string, a primitive type, or recursively a key-value pair, as shown below.

@@

The GUID is a self-certifying identifier computed as a compact one-way hash of a public key. Each name record is aliased to one or more globally unique human-readable names that are bound to the GUID by a certificate supplied by one or more {\em name certification service(s)} (NCS). Loosely speaking, the human-readable name is analogous to a DNS domain name and a name record to a zone file, but with the following important differences.

{\bf{Security.}} As shown in Fig. \ref{fig:DNS_GNS}, to initiate communication with a destination Y, an endpoint X must first obtain a certificate of the form [\verb+JohnSmith2178:Phone1+, $Y, P]_{K^-}$ that binds the human-readable name to the GUID Y and its GNS provider P, and is signed by the private key $K^-$ of an NCS that X trusts. A certificate search service (e.g., a search engine or ISP) can help index certificates from different NCSes, and help X find a certificate from a trusted NCS, and even find the human-readable name based on keywords.

{\bf{Federation.}} Unlike ICANN and root DNS servers that respectively act as a single name adjudication authority and root of trust for certification, our approach decentralizes trust across different NCS providers, potentially allowing endpoints to use quorum-based approaches to resolve conflicting name certificates. More importantly, our federation approach allows endpoints to select arbitrary human-readable names and NCS providers unlike DNS that restricts domain names to be hierarchical and federation and the DNSSEC keychain to strictly follow the name structure. An inevitable implication of decentralizing trust is that two endpoints can communicate securely only if they share a trusted NCS provider, but this change we argue is preferable to and a strict generalization of the single-root-of-trust model that some perceive as arbitrary \cite{ICANN-debate-Sems,ICANN-debate-Gross}.

%Decentralizing trust implies is that two endpoints can communicate securely only if they share a trusted NCS provider; they can always fall back to

{\bf{Extensibility.}} Our design cleanly separates the GNS provider's resource-intensive responsibility of name resolution under high mobility from the slow-changing certification process. It also allows for the GNS provider to be deployed today as a managed authoritative DNS provider (Fig. \ref{fig:DNS_GNS}) with the DNSSEC key deriving the GUID. Finally, the key-value store API enables an extensible name record representation. By default, each top-level key has associated read and write ACLs that could either be a blacklist or whitelist of GUIDs that respectively have read or write access. For example, a name record for GUID \verb+X+ that helps context-aware delivery or multihoming policies (detailed in $\S$\ref{sec:context}) is below.
\verb+{X:+
\verb+{IPs:[{IP: 23.55.66.43, plan: Unlimited}, {IP:+\\
\verb+62.44.65.75, plan: Limited}], geoloc: {[lat,long],+\\
\verb+readWhitelist:[Y,Z]}, multihome_policy:+
\verb+Unlimited}}+

@@

%For the former, it suffices to think of a {\em name} as a domain name, a {\em name record} as the associated zone file, and a {\em name server} as analogous to a DNS name server. For ease of exposition, we assume one name server per geo-location.

\subsection{\auspice's geo-distributed design}

\begin{figure}[t]
	\centering
	\vspace{-0.3in}
	\includegraphics[scale=0.33]{gns-dns/gnrs.pdf}
	\vspace{-0.35in}
	\caption{Geo-distributed name servers in \auspice.  Replica-controllers  (logically separate from active replicas) decide placement of active replicas and active replicas handle requests from end-users. N1 is a globally popular name and is replicated globally; name N2 is  popular in select regions and is replicated in those regions.}
	\vspace{-0.2in}
	\label{fig:auspice}
\end{figure}

Next, we explain how \auspice\ achieves the first three design goals. At the core of \auspice\ is a placement engine that achieves the latency, cost, and availability goals by adapting the number and locations of replicas of each name record in accordance with (1) the lookup and update request rates for the name, (2) the geo-distribution of requests for the name, and (3) the aggregate request load across all names.

%The key to ensuring high availability and flexible consistency is a two-tier consensus engine for each name; the first ``control'' tier infrequently recomputes and migrates the current set of replicas of each name record, and the second ``data'' tier upon each write or read coordinates with other replicas to ensure the necessary consistency semantics.% In addition to the placement algorithm, the design and implementation challenges we address include managing a very large number of parallel Paxos instances (one per name per tier); correctly changing Paxos group membership in a live system; efficiently routing client requests;  TBD\tbd{Need to say why challenging somewhere clearly}.

Figure \ref{fig:auspice} illustrates the placement engine. Each name is associated with a fixed number, $F$, of  \emph{replica-controllers} and a variable number of  {\em active replicas} of the corresponding name record. The name's replica-controllers are computed using consistent hashing to select $F$ consecutive or otherwise deterministic nodes along the ring {\em onto} which the hash function maps names and nodes. The replica-controllers are responsible only for determining the number and locations of the active  replicas, and the actives replicas are responsible for maintaining the actual name record and processing client requests. The replica-controllers implement a replicated state machine using Paxos \cite{LamportPaxos} in order to maintain a consistent view of the current set of active replicas.

%The key insight in \auspice\ is a placement engine to compute the number and locations of replicas of a name record  based on the lookup to update ratio of the name,  the geo-distribution of its demand, and the aggregate request load on the system.

%
%At an abstract level, \auspice\ design can be described as consisting of two planes: a ``control plane'' which determines the locations at which each name record is replicated, and a ``data plane''  consisting of  replicas of name records whose function is to handle address lookups and updates for end-users.  Physically, both these planes run across the set of name servers on which \auspice\ is deployed. 
%
%
%The role of the control plane for a name is handled by a fixed number, $M$, of  \emph{replica-controllers}. The number and locations of the replica-controllers is fixed and is computed using $M$ well-known consistent hash functions each of which maps the name to a name server location. The replica-controllers implement a replicated state machine using Paxos \cite{LamportPaxos} so as to maintain a consistent view of the current set of active replicas despite failures. 
%

%The control plane periodically runs a placement algorithm and places a name record based on the inferred pockets of demand for that name, the lookup-to-update ratio of the name, and the aggregate system load so as to achieve low lookup latency, low update cost, and desired level of availability.

% achieve low response times, low update costs, and high availability.
%based on the geo-locality of demand for that name while mitigating load hotspots across all locations.

%The key insight in \auspice\ is a placement engine to compute the number and locations of resolver replicas for a name based on the geo-locality of demand for that name while mitigating load hotspots across all locations.

@@

%Figure \ref{fig:auspice} illustrates the architecture of \auspice.  Each name is associated with a fixed number, $M$, of  \emph{replica-controllers} and a variable number of  {\em active replicas} of the corresponding resolver. The locations of the replica-controllers is fixed and computed using $M$ well-known consistent hash functions each of which maps the name to a name server location. The replica-controllers form the ``control plane'' and are responsible only for determining the number and locations of active replicas, and the active replicas are responsible for maintaining resource records and responding to lookup and update requests.

@@

A name's replica-controllers compute its active replica locations in a {\em demand-aware} manner. This computation proceeds in epochs as follows. At creation time, the active replicas are chosen to be physically at the same locations as the corresponding replica-controllers. In each epoch, the replica-controllers obtain from each active replica a summarized load report that contains the request rates for that name from different {regions} as seen by that replica. Here, {\em regions} partition users into non-overlapping groups that capture locality, e.g., IP prefixes or a geographic  partitioning based on cities; and the {\em load report} is a spatial vector of request rates as seen by the replica. The replica-controllers aggregate these load reports to obtain a concise spatial distribution of all requests for the name.

\eat{
	The replica-controllers execute Paxos to compute the placement decision in a coordinated manner for each name. During periods of graceful execution, only one replica-controller (the Paxos coordinator) actually invokes the mapping algorithm while the others simply accept its proposed placement; consensus ensures that the replica-controllers maintain a consistent view of the current set of active replicas despite failures.
}

%\begin{figure}[t]
%\begin{center}
%%\includegraphics[width=3in, height=2.4in]{Auspice-arch/Slide1}
%\includegraphics[width=3in]{graph/slide2SS}
%\vspace{-0.2in}
%\caption{\auspice\ design: Clients send typical requests to nearby active replicas of resolvers. Replica-controllers compute the number and locations of active replicas for each name based on load reports in each epoch.}
%\vspace{-0.2in}
%\label{fig:arch}
%\end{center}
%\end{figure}
\vsp
\subsubsection{Demand-aware replica placement} 
\label{sec:placement}

In each epoch, the replica-controllers use a {placement algorithm} that takes as input the aggregated load reports and capacity constraints at name servers to determine the number and locations of active replicas for each name so as to minimize client-perceived latency. We have formalized this {\em global} optimization problem as a mixed-integer program and shown it to be computationally hard.  As our focus is on simple, practical algorithms, we defer the details of the optimization approach \cite{techreport}, using it only as a benchmark in small-scale experiments with \auspice's heuristic algorithm%\tbd{Need the optimization formulation here.}.

@@

\auspice's placement algorithm is a simple heuristic  and can be run {\em locally} by each replica-controller. The placement algorithm computes the number of replicas using the lookup-to-update ratio of a name in order to limit the update cost to within a small factor of the lookup cost. The number of replicas is always kept more than the minimum number needed to meet the availability objective under failures.   The location of these replicas are decided to minimize lookup latency by placing a fraction of replicas close to pockets of high demand for that name while placing the rest randomly so as to balance the potentially conflicting goals of reducing latency and balancing load among name servers.
%The location of these replicas are decided partly based on the locality of demand, while the rest of the replicas are placed randomly in order to achieve a good tradeoff between locality-awareness and load-balance.

{
	%To this end, we develop a simple heuristic placement algorithm that is computationally efficient. Our algorithm places active replicas in a  locality- and load-aware manner by leveraging three key design insights: it creates a number of active replicas proportional to the ratio of the read rate and write rate for the name; it places some replicas at the locations that receive the highest number of requests for that name and places the rest at random locations;

	%and it redirects client requests to active replicas taking both round-trip network latency and name server load into account.

	%\bp{How we compute the number of replicas}
	Specifically, the placement algorithm computes the number of replicas for a name as ($F+ \beta r_i/w_i$), where $r_i$ and $w_i$ are the lookup and update rates of name $i$; $F$ is the minimum number of replicas needed to meet the availability goal (\S \ref{sec:design_goals}); and $\beta$ is a replication control parameter that is automatically determined by the system so as to trade off latency benefits of replication against update costs given capacity constraints as follows. In each epoch, the replica-controllers recompute $\beta$ so that the aggregate load in the system corresponds to a preset threshold utilization fraction $\mu$. For simplicity of exposition, suppose read and write operations impose the same load, and the total capacity across all name servers (in reads/sec) is $C$. Then, $\beta$ is set so that  
	\vsp
	\begin{equation}
	\mu C = \sum_i r_i  + \sum_i (F + \beta  \frac{r_i}{w_i}) w_i
	\label{eq:mu}
	\end{equation}
	\vsp
	\vsp

	where the right hand side represents the total load summed across all names. The first term in the summation above is the total read load and the second is the total write load. 
	%\begin{equation}
	%\beta = \frac{C\mu - M \sum_i W_i}{\sum_i R_i}- 1
	%\label{eq:beta}
	%\end{equation}
	%It is straightforward to extend the above heuristic to scenarios where read and write operations impose unequal amounts of load on a name server

	Having computed $\beta$ as above, replica-controllers compute the locations of active replicas for name $i$ as follows. Out of the $F + \beta r_i/w_i$ total replicas, a fraction $\nu$ of replicas are chosen based on locality, i.e., replica-controllers use the spatial vector of load reports to select $\nu(F + \beta r_i/w_i)$ name servers that are respectively the {closest} to the top $\nu(F + \beta r_i/w_i)$ regions sorted by demand for name $i$. The remaining $(1-\nu)(F + \beta r_i/w_i)$  are chosen randomly without repetition. The locality-based replicas above are chosen as the {\em closest} with respect to round-trip latency plus load-induced latency measured locally at each name server. An earlier design chose them based on round-trip latency alone, but we found that adding load-induced latencies in this step (in addition to choosing the remaining replicas randomly) ensures better load balance and lowers overall client-perceived latency.
	Our current prototype and system experiments fix the random perturbation knob $\nu$ to 0.5. We have since developed a slightly modified placement scheme that relieves the administrator from setting $\nu$ manually, automatically balancing locality-awareness and load to ensure low latencies \cite{techreport}. Thus, an administrator need only specify F and $\mu$ based on fault tolerance and aggressiveness of capacity utilization.
	%Explicitly, we compute replication parameter $\beta$ in each replication epoch to make sure the total load in the system is within a certain threshold $C$. With each name $i$ having $(\alpha + \beta \times R_i/W_i)$ replicas, where $R_i$ and $W_i$ are lookup and update rates for name $i$ respectively, the total load is the sum of lookup load and update load, i.e., 
	%\begin{equation}
	%\sum_i R_i + \sum_i (\alpha + \beta \times \frac{R_i}{W_i}) W_i
	%\end{equation}
	%To make sure this load is within the threshold $C$, we can compute $\beta$ as
	%\auspice\ uses the max value of $\beta$ that satisfy Eq \ref{eq:beta}.

	%\bp{How we place locations of replicas}
	%\auspice\ places replicas by taking into account both the geo-locality of requests and load-balancing across name servers. Replicas are selected using the votes received by a name server.  Votes for a name-server are equal to sum of requests from the geo-graphic region to which this name-server is the closest name server. The number of replicas selected based on locality is determined by the locality parameter $K$. We choose up to $K$ name servers receiving maximum number of votes as be resolvers. The remaining name servers are chosen randomly to ensure load balancing.

%\vfill\eject

%\subsubsection{Sequential consistency}
%
%- Paxos group between active replicas
%
%- role of sequence numbers
%
%- changing set of active replicas
%
%\subsubsection{Adding and deleting names}
%
%\subsubsection{Handling name server failures}

\subsubsection{Client request routing}
\label{sec:routing_client_requests}
A client request is routed from an end-host to a suitable name server as follows.
The set of all name servers in an \auspice\ instance is known to each member name server and can be obtained from a well-known location. 
End-hosts can either directly send requests to a name server or channel them through a local name server like today. 
When a local name server encounters a request for a name for the first time, it uses the known set of all name servers and consistent hashing to determine the replica-controllers for that name and sends the request to the closest replica-controller. The replica-controller returns the set of active replicas for the name and the client resends the request to the closest active replica.  In practice, we expect replica-controllers to be contacted infrequently as the set of active replicas can be cached and reused until they change in some future epoch. %, and active replicas change across epochs only if the geo-locality of demand for the name changes significantly.
%Local name server requests up to three active replicas to get a response.  A timeout value is set for every request sent and the request is sent to the next closest active replica on a timeout.

%To answer lookup requests, local name servers implement a TTL-based cache to store the name records received.

%A local name server redirects end-users requests to a resolver chosen in a locality and load-aware manner. To achieve both these properties, local name servers maintain latency estimates to name servers that reflect both network latency and server-load induced latency (or server latency). Among a set of resolvers,  a local name server always redirects requests to the closest name server based on  the latency estimates.

%A local name server in \auspice\ redirects end-users requests to a resolver chosen in a locality and load-aware manner. To achieve both these properties, local name servers maintain latency estimates to name servers that reflect both network latency and server-load induced latency (or server latency). Among a set of resolvers,  a local name server always redirects requests to the closest name server based on  the latency estimates.  Network latency estimates change slowly and therefore every local name server maintains round-trip latency estimates to all name servers using infrequent measurements. Server latency changes frequently due to dynamic workloads.  In an Internet scale deployment with tens of thousands of name servers, maintaining server latency information would add significant overhead.  Hence, server latency  is maintained only for a smaller number of frequently contacted name servers.

Network latency as well as server-load-induced latency help determine the closest replica at a local name server. Each local name server maintains an estimate of the round-trip latency to all name servers using infrequent pings; an (as yet unimplemented) optimization to reduce the overhead of all-to-all pings is to use coordinate embedding, geo-IP, or measurement-driven techniques \cite{iplane}. To incorporate load-induced latency, the latency estimate to a name server is passively measured as a moving average over lookups sent to that name server. The local name server also maintains a timeout value based on the moving average and variance of the estimates.  If a lookup request sent to a name server times out, the local name server infers that either the server or network route is congested, and it multiplicatively increases its latency estimate to that name server by a fixed factor. Thus,  if multiple lookups sent to a name server time out, the estimated latency shoots up and the local name server stops sending requests to that name  server, which effectively acts as a more agile load-balancing policy in the request routing plane (complementing the replica placement plane above that operates in coarser-grained epochs).

@@

%The above proximity-based strategy can route both lookup (or read) and update (or write) requests for a name to any active replica. In order to ensure low lookup latency, it is important for them to be served locally from an active replica. This means that the onus of replica coordination in order to maintain any nontrivial consistency semantics falls on the update procedure. But why should we care about consistency when DNS and network protocols in general prize liveness over consistency\cite{consensus-routing}?

As a global name-to-address resolution service, \auspice\ must at least ensure this eventual consistency property: {\em all active replicas must eventually return the same value of the name record and, in a single-writer scenario, this value must be the last update made by the (only) client}; ``eventually" means that there are no updates to a name record and no replica failures for sufficiently long. Violating this property means that a mobile client may be  persistently unreachable even though it is no longer moving (updating addresses).

@@

\eat{
	\subsubsection{Replica reconfiguration policies}
	\label{sec:reconf_policy}
